Czech parliament meeting recordings as ASR training data

### 2020-04-07 2020-tsd-brno-svolocz/svolocz.tex
new minimum start/end reliability 70%

\begin{enumerate}
\item{The first and last token have reliability at least 50\%,}
\item{The mean reliability of all tokens is at least 70\%,}
\item{The number of words is no less than five.}
\end{enumerate}

@@

All the constants and criteria are to be considered a baseline solution. They
all could be tweaked much more rigorously and solved much more soundly. However,
this simple solution readily yields a high-quality training dataset of 1058
hours. Of the total 542,610 segments, 166,458 (31\%) have been accepted to the
training dataset. Of the total 376,152 discarded segments, 316,030 (84\%) were
discarded because of the criterion of unreliable start or end.

Setting the minimum reliability of the boundary words from 50\% to 70\% reduces
the number of accepted chunks to by 17\%. It strips 5\% segments
of the total number from the dataset. But if we consider that 40\% of the total
number of segments must be discarded because of audio padding, the loss is
acually 9\%. It is an option to raise the matching reliability with a cost of
training data volume.

>>>>

\begin{enumerate}
\item{The first and last token have reliability at least 70\%,}
\item{The mean reliability of all tokens is at least 70\%,}
\item{The number of words is no less than five.}
\end{enumerate}

@@

All the constants and criteria are to be considered a baseline solution. They
all could be tweaked much more rigorously and solved much more soundly. However,
this simple solution readily yields a high-quality training dataset of 1058
hours. Of the total 539,057 segments, 142,530 (26\%) have been accepted to the
training dataset. Of the total 396,527 discarded segments, 350,258 (88\%) were
discarded because of the criterion of unreliable start or end.

Reducing the minimum reliability of the boundary words from 70\% to 50\% increases
the number of accepted chunks by 17\%. It adds 5\% segments
of the total number to the dataset. But if we consider that 40\% of the total
number of segments must be discarded because of audio padding, the gain is
acually 9\%. It is an option to increase the training data volume at the cost
of matching precision.
